```{r}
library(tidyverse)
library(janitor)
library(lubridate)
library(rvest)
```


```{r}
season_23_24 <- nba_2324 %>% 
  clean_names() %>% 
  rename(team = tm,
         three_ptm = x3p,
         three_pa = x3pa,
         three_percent = x3p_percent) %>% 
  mutate(season = "2023-24")
```

First grouping and iding the number of players on two teams
```{r}
over_100_threes <- season_23_24 %>% 
  filter(three_ptm >= 100) %>% 
  arrange(desc(three_ptm))
```

Removing tots because it shows a players total threes and not their one for a specific team
```{r}
over_100_threes <- over_100_threes %>% 
  filter(team != "TOT")

```

Now grouping to see the teams in 23-24
```{r}
over_100_2324 <- over_100_threes %>% 
  group_by(team) %>% 
  summarize(players_2324 = n()) %>% 
  arrange(desc(players_2324))

```

Next step
I want to try and scrape other years and run the same code chunks as above so I can see the amount of players with over 100 3pointers on each team. I want the final product to look like a table with teams on the y axis and season on the x axis.






