```{r}
# libraries
library(tidyverse)
library(lubridate)
library(janitor)
```

What do I want to accomplish?
- I want to see how Iowa guard Caitlin Clark performed against other teams during her career.
- We can have this data timely for when the tournament comes around.

Cleaning Steps
- Import data
- Clean columns and remove the bottom one
- label home and away in the proper column
- do group_by and summarize on the important data points

Questions to answer
- What team does Caitlin Clark perform best against
- How many points (total points) has she scored against each team (and avg)
- How many assists, rebounds 3PM, 3p% etc... other relevant stats
- What conference does she do best against?
- How does she do against only Big Ten teams. 


```{r}
#import data
clark_logs <- read_csv("data/clark_logs.csv")

```

----------- Cleaning Data -----------------

```{r}
#cleaning names and columns
clark_logs_cleaned <- clark_logs %>% 
  clean_names() %>% 
  rename(home_away = x5,
         W_L = x8,
         two_ptm = x2p,
         two_pta = x2pa,
         two_fg_perc = x2p_percent,
         three_pm = x3p,
         three_pa = x3pa,
         three_fg_perc = x3p_percent) %>% 
  slice(1:129)

#replace NA in home_away with H

clark_logs_cleaned <- clark_logs_cleaned %>%
  mutate(home_away = case_when(
    is.na(home_away) ~ "H",
    TRUE ~ home_away
  ))

```

------------ Data exploration ---------------

### Aggregating the points

```{r}

clark_logs_cleaned %>% 
  group_by(opponent) %>% 
  summarize(total_minutes = sum (mp),
            total_points = sum(pts),
            total_reb = sum(trb),
            total_ast = sum(ast),
            
            ) %>% 
  arrange(desc(total_minutes))

```





