```{r}
# libraries
library(tidyverse)
library(lubridate)
library(janitor)
```

What do I want to accomplish?
- I want to see how Iowa guard Caitlin Clark performed against other teams during her career.
- We can have this data timely for when the tournament comes around.

Cleaning Steps
- Import data
- Clean columns and remove the bottom one
- label home and away in the proper column
- do group_by and summarize on the important data points

Questions to answer
- What team does Caitlin Clark perform best against
- How many points (total points) has she scored against each team (and avg)
- How many assists, rebounds 3PM, 3p% etc... other relevant stats
- What conference does she do best against?
- How does she do against only Big Ten teams. 


```{r}
#import data
clark_logs <- read_csv("data/clark_logs.csv")

```

----------- Cleaning Data -----------------

```{r}
#cleaning names and columns
clark_logs_cleaned <- clark_logs %>% 
  clean_names() %>% 
  rename(home_away = x5,
         W_L = x8,
         two_ptm = x2p,
         two_pta = x2pa,
         two_fg_perc = x2p_percent,
         three_pm = x3p,
         three_pa = x3pa,
         three_fg_perc = x3p_percent) %>% 
  slice(1:136)
```


```{r}
#replace NA in home_away with H

clark_logs_cleaned <- clark_logs_cleaned %>%
  mutate(home_away = case_when(
    is.na(home_away) & type == "REG" ~ "H",
    type == "CTOURN" ~ "N",
    type == "ROUND-64" ~ "H",
    type == "ROUND-32" ~ "H",
    TRUE ~ home_away
  ))




```

Clark games against each team

```{r}

#creating a b10 list

big10 <- c("Nebraska", "Minnesota", "Illinois", "Northwestern", "Wisconsin", "Indiana", "Purdue", "Ohio State", "Michigan", "Michigan State", "Penn State", "Rutgers", "Maryland")

games_per_team <- clark_logs_cleaned %>% 
  group_by(opponent) %>% 
  summarize(total_games = n()) %>% 
  arrange(desc(total_games))

```


------------ Data exploration ---------------

### Aggregating the points

## Try to get the per games

```{r}
#aggregate total analysis
totals_clark_logs <- clark_logs_cleaned %>% 
  group_by(opponent) %>% 
  summarize(total_minutes = sum (mp),
            total_points = sum(pts),
            total_reb = sum(trb),
            total_ast = sum(ast),
            total_3pm = sum(three_pm),
            total_3pa = sum(three_pa)) %>% 
  arrange(desc(total_points))

#joining

clark_logs_and_games <- inner_join(totals_clark_logs, games_per_team, by = "opponent")

# per game anaysis

per_game_clark_logs <- clark_logs_and_games %>% 
  group_by(opponent) %>% 
  mutate(ppg = (total_points/total_games),
         rpg = (total_reb/total_games),
         apg = (total_ast/total_games),
         threes_made_pg = (total_3pm/total_games),
        threes_attempted_pg  = (total_3pa/total_games),
        mpg = (total_minutes /total_games))
```


Clark home vs. away
```{r}
clark_logs_cleaned %>%
  filter(type == "REG") %>% 
  group_by(home_away) %>% 
  summarize(total_minutes = sum (mp),
            total_games = n(),
            total_points = sum(pts),
            total_reb = sum(trb),
            total_ast = sum(ast),
            total_3pm = sum(three_pm),
            total_3pa = sum(three_pa)) %>% 
  mutate(ppg = (total_points/total_games),
         rpg = (total_reb/total_games),
         apg = (total_ast/total_games),
         threes_made_pg = (total_3pm/total_games),
        threes_attempted_pg  = (total_3pa/total_games),
        mpg = (total_minutes /total_games))
```

clark in NCAA T
```{r}

clark_logs_cleaned %>% 
  filter(type != "REG", type != "CTOURN") %>% 
  group_by(season) %>% 
  summarize(total_minutes = sum (mp),
            total_games = n(),
            total_points = sum(pts),
            total_reb = sum(trb),
            total_ast = sum(ast),
            total_3pm = sum(three_pm),
            total_3pa = sum(three_pa)) %>% 
  mutate(ppg = (total_points/total_games),
         rpg = (total_reb/total_games),
         apg = (total_ast/total_games),
         threes_made_pg = (total_3pm/total_games),
        threes_attempted_pg  = (total_3pa/total_games),
        mpg = (total_minutes /total_games))
```

