```{r}
library(tidyverse)
library(janitor)
library(lubridate)
#install.packages("remotes")
#remotes::install_github("slu-openGIS/postmastr")
#library(postmastr)
library(usdata)
library(rvest)
library(ggplot2)
library(ggalt)
#install.packages("ggtext")
library(ggtext)
library(htmltools)
```

Theses numbers and all attribution is from the University of Maryland's Sports Roster Data Project.


```{r}
# Loading player data from 2022-2023
wbb23_24_rosters <- read_csv("data/wbb_rosters_2023_24.csv")
wbb22_23_rosters <- read_csv("data/wbb_rosters_2022_23.csv")
```

The countries that need to be cleaned are "The Netherlands and BOSNIA AND HERZEGOVINA" NOTE: I replaced the 23_24 file with the one Derek updated: this is a link to the file. <https://github.com/Sports-Roster-Data/womens-college-basketball/blob/main/wbb_rosters_2023_24.csv>

```{r}
wbb22_23_rosters <- wbb22_23_rosters %>% 
  mutate(
    country_clean = case_when(
      country_clean == "THE NETHERLANDS" ~ "NETHERLANDS",
      country_clean == "BOSNIA AND HERZEGOVINA" ~ "BOSNIA & HERZEGOVINA",
      TRUE ~ as.character(country_clean)))
```

Creating power 5 list

```{r}
power_5 <- c("ACC", "Big 12", "Big Ten", "Pac-12", "SEC")
```

Filtering for non us players

```{r}
non_us_22_23 <- wbb22_23_rosters %>%
filter(country_clean != "USA", division == "I")
  
non_us_23_24 <-  wbb23_24_rosters %>% 
  filter(country_clean != "USA", division == "I")

```


```{r}
#23-24
teams_with_int_players_23_24 <- non_us_23_24 %>% 
  group_by(ncaa_id, team, conference) %>% 
  summarize(int_players = n()) %>% 
  arrange(desc(int_players))

#22-23
teams_with_int_players_22_23 <- non_us_22_23 %>% 
  group_by(ncaa_id, team, conference) %>% 
  summarize(int_players = n()) %>% 
  arrange(desc(int_players))

# total players
total_player_23_24 <-  wbb23_24_rosters %>% 
  filter(division == "I") %>% 
  group_by(ncaa_id, team, conference) %>% 
  summarize(total_players = n()) %>% 
  arrange((team))

total_player_22_23 <- wbb22_23_rosters %>% 
  filter(division == "I") %>% 
  group_by(ncaa_id, team, conference) %>% 
  summarize(total_players = n()) %>% 
  arrange((team))

# this shows the missing team from 23-24 is Florida State
list <- anti_join (total_player_22_23, total_player_23_24, by= "team")
```

# need to figure out a new way to get a clean version of all players.

# I need to do the left joins in seperate years and then do the mutates for the NA values, then inner joins back together.

```{r}
 
all_players23_24 <- left_join(total_player_23_24, teams_with_int_players_23_24, by = "ncaa_id")

all_players22_23 <- left_join(total_player_22_23, teams_with_int_players_22_23, by = "ncaa_id")

all_players <- inner_join(all_players23_24, all_players22_23, by = "ncaa_id")

```

```{r}
# cleaning the all_players df
all_players <- all_players %>% 
  rename(team = team.x.x,
         conference = conference.x.x,
         total_23_24 = total_players.x,
         int_players_23_24 = int_players.x,
         total_22_23 = total_players.y,
         int_players_22_23 = int_players.y) %>% 
select(ncaa_id, team, conference, int_players_23_24, int_players_22_23, total_23_24, total_22_23, -team.y.x, -team.y.y, -team.y.y)

# fixing NAs
all_players <- all_players %>%
  mutate(
    int_players_23_24 = case_when(
      is.na(int_players_23_24) ~ 0,
      TRUE ~ int_players_23_24),
    int_players_22_23 = case_when(
      is.na(int_players_22_23) ~ 0,
      TRUE ~ int_players_22_23))
```

adding in percentages

```{r}
# Percentage change doesn't show anything interesting here. Percentages does.

all_players <- all_players %>% 
  mutate(int_diff = int_players_23_24 - int_players_22_23,
         int_player_perc_23_24 = int_players_23_24/total_23_24*100,
         int_player_perc_22_23 = int_players_22_23/total_22_23*100)
```


------- Data Exploration Section -----------

Here I will answer the obvious outstanding questions and try to formulate a story narrative after it.

Which conference has most players

```{r}
# totals per conf
conf_counts23_24 <- non_us_23_24 %>% 
  filter(division == "I") %>% 
  group_by(conference) %>% 
  summarize(players_23_24 = n())
  
  conf_counts_22_23 <- non_us_22_23 %>% 
  filter(division == "I") %>% 
  group_by(conference) %>% 
  summarize(players_22_23 = n())
  
  total_conf <- inner_join(conf_counts23_24, conf_counts_22_23, by = "conference")
  
  #internationals
by_conf <- all_players %>% 
  group_by(conference) %>% 
  summarise(int_players_23_24 = sum(int_players_23_24),
            int_players_22_23 = sum(int_players_22_23))
#joining
all_conf <- inner_join(by_conf, total_conf, by="conference")

all_conf <- all_conf %>%  
  mutate(diff= int_players_23_24 - int_players_22_23,
         conf_perc_23_24 = int_players_23_24/sum(int_players_23_24)*100,
         conf_int_perc_22_23 = int_players_22_23/sum(int_players_22_23)*100)
```

which countries produce the most players

```{r}
#23-24
countries_23_24 <- non_us_23_24 %>% 
    group_by(country_clean) %>% 
  summarize(int_players = n()) %>% 
  arrange(desc(int_players))

#22-23
countries_22_23 <- non_us_22_23 %>% 
    group_by(country_clean) %>% 
  summarize(int_players = n()) %>% 
  arrange(desc(int_players))

# joining
total_country <- inner_join(countries_23_24, countries_22_23, by = "country_clean")

total_country <- total_country %>% 
  rename(int_players_23_24 = int_players.x,
         int_players_22_23 = int_players.y) %>% 
  mutate(diff = int_players_23_24 - int_players_22_23,
         perc_23_24 = int_players_23_24/sum(int_players_23_24)*100,
         perc_22_23 = int_players_22_23/sum(int_players_22_23)*100,
  perc_change = ((int_players_23_24 - int_players_22_23) / int_players_22_23) * 100)

# per team
non_us_22_23 %>% 
  filter(team == "South Florida") %>% 
  group_by(country_clean) %>% 
  summarize(int_players = n()) %>% 
  arrange(desc(int_players))


```


--------------- Labeling tournament teams -------------------
Steps
- on the `all_players` df, add two columns. One called ncaat23_24 and one called ncaat22_23.
- write a case_when to put y if they were a tournament team and a n if they were not in 2023... do the same for 23-24
- Then filter teams that were a tourney team and had >0 international players.

```{r}
# 22-23 tournament teams

# Confirmed this now is 68 teams


ncaat_22_23 <- c("Arizona", "Creighton", "Holy Cross", "Illinois", "Marquette", "Maryland", "Mississippi State", "Norfolk State", "Notre Dame", "Oklahoma", "Portland", "Sacramento State", "South Carolina", "South Florida", "Southern Utah", "UCLA", "West Virginia", "Alabama", "Baylor", "Chattanooga", "Iowa State", "James Madison", "North Carolina", "Ohio State", "Purdue", "Saint Louis", "South Dakota State", "St. John's", "Tennessee", "Toledo", "UConn", "Southern Cal", "Vermont", "Virginia Tech",  "Cleveland State", "Florida Gulf Coast", "Gardner-Webb", "Hawaii", "Indiana", "LSU", "Miami", "Michigan", "Monmouth", "NC State", "Oklahoma State", "Princeton", "Tennessee Tech", "UNLV", "Utah", "Villanova", "Washington State", "Colorado", "Drake", "Duke", "East Carolina", "Florida State", "Georgia", "Gonzaga", "Iona", "Iowa", "Louisville", "Middle Tennessee", "Mississippi", "Sacred Heart", "Southeastern Louisiana", "Southern", "Stanford", "Texas")
```


```{r}

ncaat23_24 <- c("Sacred Heart", "Presbyterian College", "Vanderbilt", "Columbia", "Auburn", "Arizona", "Holy Cross", "UT Martin", "North Carolina", "Michigan State", "Ohio State", "Maine", "Louisville", "Middle Tennessee", "South Carolina", "Duke", "Richmond", "Texas", "Drexel", "Virginia Tech", "Marshall", "LSU", "Rice", "Kansas State", "Portland", "Alabama", "Florida State", "Baylor", "Colorado", "Drake", "Iowa State", "Maryland", "Oregon State", "Eastern Washington", "Stanford", "Norfolk State", "Nebraska", "Texas A&M", "Tennessee", "Green Bay", "UConn", "Jackson St.", "Indiana", "Fairfield", 
"Kansas", "Michigan", "Notre Dame", "Kent State", "NC State", "Chattanooga", "Iowa", "Syracuse", "Oklahoma", "Florida Gulf Coast", "Southern Cal", "A&M-Corpus Christi", "Mississippi", "Marquette", "West Virginia", "Princeton", "Creighton", "UNLV", "Gonzaga", "UC Irvine", "UCLA", "California Baptist", "Utah", "South Dakota State")
```


```{r}
# putting a y or n if a school was a tourney team in 22-23
ncaat_teams <- all_players %>%
  mutate(tourny_team_22_23 = case_when(
    team %in% ncaat_22_23 ~ "y",
    TRUE ~ "n"
  ))
```


```{r}
#Filtering to see what the tourney teams looked like w internationals
# Unsure of why this produces 67 and not 68
ncaa_yes22_23 <- ncaat_teams %>% 
  filter(tourny_team_22_23 == "y") %>% 
  select(team, conference, int_players_22_23, total_22_23, int_players_22_23, int_player_perc_22_23) %>% 
  arrange(desc(int_player_perc_22_23))
```


```{r}
# doing the same process for 2024
#adding column 

ncaat_teams_both_yrs <- ncaat_teams %>%
  mutate(tourny_team_23_24 = case_when(
    team %in% ncaat23_24 ~ "y",
    TRUE ~ "n"
  ))

# 23-24 teams international list
# Unsure of why this produces 66 teams and not 68?... Im assuming that it is the same reason the 22-23 list produced 67?
ncaa_yes23_24 <- ncaat_teams_both_yrs %>% 
  filter(tourny_team_23_24 == "y") %>% 
  select(team, conference, int_players_23_24, total_23_24, int_players_23_24, int_player_perc_23_24) %>% 
  arrange(desc(int_player_perc_23_24))


```

Which teams both have yes
```{r}

ncaat_both_yrs_yes <- ncaat_teams_both_yrs %>% 
  filter(tourny_team_23_24 == "y", tourny_team_22_23 == "y")

```






